Software Architectures for Integrating Workflow Engines in Science Gateways

### 2016-05-13 paper.tex
now it is true, done with 3.6

\paragraph{Robustness} The two workflow services are specific to
workflow execution (\texttt{R$_1$=2}). Interactions \texttt{b}
(twice), \texttt{c$_2$} (twice) and \texttt{d} (twice) also
are (\texttt{R$_2$=6}).
\closednote{Marc-e}{I understand both points. However, complexity is
  addressed in Robustness as well... I liked the idea of development effort. It's a tough call.}{Tristan}{Maybe 'integration challenge' is a good compromise.}

\paragraph{Extensibility} Adding a new type of \emph{parent} engine
requires to implement the corresponding service, to implement
interactions \texttt{b} and \texttt{c$_2$} in the parent engine, and
to implement interaction \texttt{d} in the science gateway and in the
parent service (\texttt{E$_1$=5}). Adding a new type of \emph{child}
engine only requires to implement the corresponding service, to
develop interactions \texttt{b} and \texttt{c$_2$} in the child
engine, and to implement interaction \texttt{d} in the parent service
(\texttt{E$_1$=4}). We use \texttt{E$_1$=4.5} in
Table~\ref{table:evaluation} to reflect both conditions. Adding a new
version in the parent or child engine only requires modifying this
engine (\texttt{E$_2$=0}). Adding a new workflow is done through
interaction \texttt{a$_1$} and \texttt{a$_2$}
(\texttt{E$_3$=2}). Adding a new infrastructure requires to
re-implement interactions \texttt{a$_1$}, \texttt{b} and
\texttt{c$_2$} twice, and interaction \texttt{c$_1$} once so that it
can be supported by both workflow engines (\texttt{E$_4$=6}).

>>>>

\paragraph{Robustness} The two workflow services are specific to
workflow execution (\texttt{R$_1$=2}). Interactions \texttt{b}
(twice), \texttt{c$_2$} (twice) and \texttt{d} (twice) also
are necessary (\texttt{R$_2$=6}).
\closednote{Marc-e}{I understand both points. However, complexity is
  addressed in Robustness as well... I liked the idea of development effort. It's a tough call.}{Tristan}{Maybe 'integration challenge' is a good compromise.}

\paragraph{Extensibility} Adding a new type of \emph{parent} engine
requires implementing the corresponding service,  implementing
interactions \texttt{b} and \texttt{c$_2$} in the parent engine, and
implementing interaction \texttt{d} in the science gateway and in the
parent service (\texttt{E$_1$=5}). Adding a new type of \emph{child}
engine only requires implementing the corresponding service, 
developing interactions \texttt{b} and \texttt{c$_2$} in the child
engine, and implementing interaction \texttt{d} in the parent service
(\texttt{E$_1$=4}). We use \texttt{E$_1$=4.5} in
Table~\ref{table:evaluation} to reflect both conditions. Adding a new
version in the parent or child engine only requires modifying this
engine (\texttt{E$_2$=0}). Adding a new workflow is done through
interaction \texttt{a$_1$} and \texttt{a$_2$}
(\texttt{E$_3$=2}). Adding a new infrastructure requires 
re-implementing interactions \texttt{a$_1$}, \texttt{b} and
\texttt{c$_2$} twice, and interaction \texttt{c$_1$} once so that it
can be supported by both workflow engines (\texttt{E$_4$=6}).
